---
title: Academic Curriculum Vitae
author: Anthony Kimpton
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pagedown::html_resume:
    css: 
      - override.css         # OVERIDE CERTAIN FUNCTIONS OF CSS
      - resume               # DEFAULT FILE
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: false
# uncomment this line to produce HTML and PDF in RStudio:
knit: pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE)
library(scholar)
library(tidyverse)
library(janitor)
library(stringr)
```

```{r guides, eval=FALSE}
# guide for this resume template
browseURL("https://towardsdatascience.com/create-your-resume-with-pagedown-package-in-r-123ca6310d52")

# api for keywords and ranked importance
browseURL("https://api.emsidata.com/apis/skills")

# site for icons
browseURL("https://fontawesome.com/")

# testing resume
browseURL("https://resumeworded.com/results-v2")
browseURL("https://www.jobscan.co/results/16564079")

# linked in tools
browseURL("https://www.linkedin.com/pulse/rlinkedin-more-long-life-linkedin-api-network-analysis-jerad-acosta")
```

```{r publications, include=FALSE}
# Define the id for Anthony Kimpton
id <- "IUqlsCwAAAAJ"

# Get his profile and print his name
profile <- get_profile(id)

h_index <- profile$h_index

total_cites <- profile$total_cites

# Get his citation history, i.e. citations to his work in a given year 
citation_history  <- get_citation_history(id)

# Get his publications (a large data frame)

clean_fn <- function(x) {
  x %>% 
  mutate(
    journal = str_to_title(journal),
    journal = str_replace_all(journal, "And", "and"),
    journal = str_replace_all(journal, "In ", "in "),
    journal = str_replace_all(journal, "Of", "of"),
    journal = str_replace_all(journal, "To", "to"),
    journal = str_replace_all(journal, "The", "the"),
    journal = str_replace(journal, "Parking", "Parking: an International Perspective"),
    journal = str_replace(journal, " Media Group", ""),
    journal = str_replace(journal, " Media Trust", ""),
    journal = str_replace(journal, "^the", "The"),
    journal = ifelse(journal == "", NA, journal))  
}

publications <- get_publications(id) %>%
  clean_names() %>%
  drop_na(year) %>% 
  transmute(
    title = str_to_sentence(title),
    title = str_replace(title, "person level integrated data asset (plida)", "Person Level Integrated Data Asset (PLIDA) of Australia"),
    title = str_replace(title, "australia", "Australia"),
    title = str_replace(title, "brisbane", "Brisbane"),
    title = str_replace(title, "covid", "COVID"),
    title = str_replace(title, "park ‘n’ride", "Park ‘n’ Ride"),
    title = str_replace(title, "pnr", "PnR"),
    author = str_replace(author, "A Kimpton", "**A Kimpton**"),
    author = sub(",([^,]*)$", " &\\1", author),
    journal,
    cites,
    year,
    formated_cites = ifelse(cites == 0, "", paste0("(cites = ", cites, ")")),
    formatted_title = paste0(title, " ", formated_cites)
  ) %>%
  clean_fn() %>% 
  drop_na(journal) %>% 
  arrange(desc(year), desc(cites))

media <- publications %>% 
  filter(grepl("The Conversation", journal))

publications <- publications %>% 
  filter(!grepl("The Conversation", journal)) 
  
rank <- get_journalrank(journals=publications$journal) %>% 
  clean_names() %>% 
  transmute(journal,
            sjr_best_quartile = as.character(sjr_best_quartile),
            sjr_best_quartile = ifelse(sjr_best_quartile != "Q1", NA, "(SJR = Q1)"),
            categories) %>%
  clean_fn() %>% 
  drop_na()

publications <- publications %>% 
  #left_join(impact, by = "journal") %>% 
  left_join(rank, by = "journal") %>% 
  mutate(formated_journal = paste0("*", journal, "*"),
         formated_journal = ifelse(is.na(sjr_best_quartile),  formated_journal, paste0(formated_journal, " ", sjr_best_quartile)),
         row = row_number())

coauthor_network <- get_coauthors(id)


pub_stat <- function(y) {
  publications %>% filter(row == x) %>% slice_head(n = 1) %>% pull(y)
}
```

Aside
================================================================================

Contact Info {#contact}
--------------------------------------------------------------------------------

- <i class="fa fa-envelope"></i> [a.kimpton@uq.edu.au](a.kimpton@unisq.edu.au)
- <i class="fa fa-github"></i> [https://github.com/akimpt](https://github.com/akimpt)
- <i class="fa fa-phone"></i> +61 412 452 471
- For more information, please contact me via email.

Skills {#skills}
--------------------------------------------------------------------------------

- Planning policy, geospatial, temporal, textual, and machine learning statistical modelling

- Advanced capabilities with R, Stata, ArcGIS, Python, SQL, and to a lesser extent, Bash, Docker, HTML, and CSS

- Streamlined Github and rMarkdown workflow for generating and updating manuscripts, reports (including this CV), presentations, APIs, interactive web pages and software.

Main
================================================================================

Anthony Kimpton {#title}
--------------------------------------------------------------------------------

<h5>Academic Curriculum Vitae</h5>

Anthony is an urban and regional planner with advanced geospatial statistics expertise, and a former Senior [MADIP](https://www.abs.gov.au/about/data-services/data-integration/integrated-data/multi-agency-data-integration-project-madip) Data Specialist with the Australian Bureau of Statistics where they trained and supervise data scientists within the Big Data Pathways section. They are excited by the promise of smart cities and a socially sustainable global society starting from the neighbourhood-scale. Their overarching career objective is clearing the open and big data expertise barrier so that urban researchers and the public can co-design liveable cities where socially diverse communities can thrive.

Anthony's research productivity and impact are exceptional relative to research opportunity. For instance, his H-Index is 12, his peer-reviewed research productivity is 164% (23/14) and citation rate is 870% (609/70) of the Australian Level-B planning academic average ([Pojani et al. 2022](https://journals.sagepub.com/doi/abs/10.1177/0739456X18804330); Google Scholar 22/04/25). He has 20 publications listed on SciVal including 12 in the top 10% of journals, 2 among the top 10% of cited papers, and an average field weighted citation impact of 2.50 in land use and transport planning (SciVAl 12/06/25). They also rank in the top 1% worldwide prominence percentile in fields including electric vehicle adoption, health disparity, physical activity, demography, and residence characteristics; and the top 2% in fields including land use, urban transportation, eScooters and Transportation.

Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Doctor of Philosophy
The University of Queensland’s School of Earth and Environmental Sciences

Brisbane, Australia

2018

**Thesis**: "The Sociability of Urban Greenspace: An Exploration of How Public Parks and Private Backyards Influence the Social Sustainability of Urban Communities" entailing the development of the first quantitative social sustainability measure, and employing social survey, crime incidence, remote imagery, administrative, and population census data to examine how public greenspace and backyards influence the neighbourhood social sustainability

**Geography & Sociology**: Logistic, negative binomial, and linear regression, cluster analysis using Stata 

### Bachelor of Arts Honours (1st class)

The University of Queensland’s School of Social Sciences

Brisbane, Australia

2012

**Thesis**: "Seeing Green: Can the Objective Physical Environment Predict Place Attachment?" employing social survey, crime incidence, census, and administrative data to examine how public greenspace influences place attachment   

**Sociology**: Multi-level statistical modelling; research design and scoping

### Bachelor of Arts

The University of Queensland’s School of Social Sciences

Brisbane, Australia

2011

**Sociology & Archaeology**: Statistical modelling using Stata and Excel; qualitative interviewing methods; geo-spatial analysis or GIS  using ArcGIS; field work; laboratory methods and procedures

Grants and Awards {data-icon=trophy}
--------------------------------------------------------------------------------

### Stellar Award Commendation

University of Southern Queensland

Springfield, Australia

2024

### $89,342 [High Impact Projects Grant](https://aurin.org.au/about-aurin/projects/aurin-high-impact-projects/)

The Australian Urban Research Infrastructure Network

Melbourne, Australia

2021

**Aim**: Lead the development of the Green Australian Vehicle Ownership (GreenAVO) service that harvests and links Australian state and territory vehicle registration APIs with vehicle characteristics from the Australian Green Vehicle Guide API to reveal spatiotemporal trends in vehicle ownership at the postcode-level for tracking, predicting, and accelerating the national transition towards hybrid and electric vehicles through strategic planning and infrastructure.

### [Dean's Award for Outstanding HDR Thesis](https://my.uq.edu.au/information-and-services/higher-degree-research/my-thesis/deans-award-outstanding-hdr-theses)

The University of Queensland’s Graduate School

N/A

2020

**Criteria**: Both thesis examiners Professors Alexis Comber and Kate Bowers commending the 2018 thesis as an outstanding theoretical, empirical, and applied research contribution requiring no changes.

### Early Career Researcher Travel Grant

The Institute of Australian Geographers

N/A

2020

**Aim**: Competitive grant funding travel to the 2020 International Geographical Union conference in Turkey (cancelled due to COVID)  

### Early Career Researcher Grant

The University of Queensland’s School of Earth and Environmental Sciences 

N/A

2019

**Aim**: Competitive grant for travel and registration to present at the 2019 Australian Sociological Association conference

### Australian Postgraduate Award

The Australian Research Council 

N/A

2019

**Aim**: Competitive grant providing $24,653 per annum throughout PhD candidature

Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

### Lecturer of Urban and Regional Planning

The University of Southern Queensland 

Springfield, Australia

present - 2023

**Role**: Researcher (0.2FTE) focusing on the intersection between land use and transport planning, and identifying the barriers to walking, cycling public transport, and public physical activity, and accessing the social equity of land use and transport planning outcomes.

### MADIP Data Specialist

The Australian Bureau of Statistics' Big Data Pathways Section 

Brisbane, Australia

2023 - 2022

**Role**: Investigate the extent to which government records can replace survey content collected by the Australian Bureau of Statistics. They are currently investigating dwelling structure and location (ABS big data), income tax records (ATO big data), and government payments (DSS and DVA big data) to replace over 120 survey questions collected from 45k Australians every 2 years. Further,  they supervise graduate data scientists investigating disability (NDIS big data) and concession card (DSS big data).

### Postdoctoral Research Fellow

The University of Queensland’s School of Earth and Environmental Sciences 

Brisbane, Australia

2022

**Role**: Investigate Australian international and internal migration, migration policy, visa types and regional retention  of immigrants using the ABS MADIP service and primarily the Traveller module with the R (programming language) for all GIS, statistical modelling, and reporting.  

### Software Developer

The Australian Urban Research Infrastructure Network and the University of Queensland’s School of Civil Engineering 

Brisbane, Australia

2021

**Role**: Develop microservices (AGILE software development) for the Australian Transport Research Cloud e.g, interactive graphics and dashboards, and application programming interfaces (API) for the public and collaborating universities using R (programming language), Docker for containerisation, and Bash for AURIN Virtual Machine operations   

### Postdoctoral Research Fellow

The Queensland Department of Transport and Main Roads & The University of Queensland’s School of Earth and Environmental Sciences 

Brisbane, Australia

2020 - 2018

**Role**: Review Australian land use and transport policy, examine land use and census data to determine how parking supply aligns with policy and influences urban mobility using the R (programming language) for all GIS, statistical modelling, and reporting including the following project page: [https://parks-uq.github.io/](https://parks-uq.github.io/)  

### Research Assistant

The University of Queensland’s School of Geography, Planning, and Environmental Management 

Brisbane, Australia

2018 - 2013

**Role**: Review community sociology and environmental criminology research literature focusing on how natural disasters impact community sociability, and examine social survey, crime incident, census, flood, and administrative data using ArcGIS for spatial analyses and cartography, and Stata for statistical modelling and data visualization

Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Lecturer of Urban and Regional Planning

The University of Southern Queensland 

Springfield, Australia

present - 2023

**Role**: Lecturer currently teaching (0.7FTE) planning structures and statutory planning, regional planning, sustainable urban design and development, and planning theory. Notably nominated and awarded the UniSQ *Stella Award for Teaching* while having receiving a 6 course load during first 12 months of appointment and while maintaining a high research output rate that nears triple the UniSQ Level B employee expectations framework. My teacching delivery raised the URP3201 end of semester mean from 3.6 (2023; n = 14) to 4.1 (2024; n = 13) immediately upon staring at UniSQ. 

::: concise
- **SVY3302: Property Valuation and Development**: Develop and present lectures on property valuation theory and methods
- **URP2001: Planning Structures and Statutory Planning**: Develop and present lectures on the role of statutory planning throughout the 3 tiers of Australian  Government
- **URP3200: Regional Planning**: Develop and deliver lectures on regional strategic planning
- **URP3201: Sustainable Urban Design and Planning**: Develop and deliver lectures on sustainability audits and master plan design
- **URP4002: Planning Theory**: Develop and deliver lectures on the theoretical and historical foundations of the planning profession
:::


### Research Supervisor 

The University of Southern Queensland’s School of Surveying and Built Environment  

Brisbane, Australia

present - 2023

Primary supervisor for 2 PhD projects, 1 masters, 4 honours, and 1 completed honours project. Associate supervisor for 1 PhD project and 1 masters project. These span disciplines including land use and transport planning, heritage management, civil engineering, and public health where I contribute planning, policy, social science and geospatial analytics expertise.


### Research Supervisor

The University of Queensland’s School of Civil Engineering & School of Earth and Environmental Sciences 

Brisbane, Australia

2023 - 2021

Associate supervised 2 PhD candidates to completion and 1 honours student


### Sessional Lecturer 

The University of Queensland’s School of Earth and Environmental Sciences 

Brisbane, Australia

2021 - 2016

**Teaching Evaluations**: Ranging 4.2 to 4.5 on a 5-point scale with 4.3 most recently awarded for both online and face-to-face delivery 

::: concise
- **GEOG1000: Human Settlements**: Develop and present lectures on the history of human settlements and future of cities to over 200 first-year urban planning, geography, and environmental management students per semester
- **GEOG2202/GEOG7202: Global Population Issues**: Develop and deliver lectures on global demographic challenges to over 60 second-year and postgraduate urban planning and geography students per semester
- **GEOG3003: The Global Metropolis**: Invited for first lecturing assignment to revamp and re-badge the “GEOG3030: the Asian Metropolis” capstone course by developing and delivering six new lectures on topics including smart cities, transport, and sustainability to over 40 final-year urban planning and geography students per semester
:::

### School Representative

The University of Queensland’s School of Earth and Environmental Sciences 

Brisbane, Australia

2017 - 2016

**Role**: Invited and employed to develop and deliver presentations at high schools, career open days, and high school teaching conferences to promote geography, planning, environmental management, and geology

### Lead Tutor/Demonstrator 

The University of Queensland’s School of Earth and Environmental Sciences & School of Social Sciences

Brisbane, Australia

2018 - 2013

**Teaching Evaluations**: Ending with 4.7 on a 5-point scale for face-to-face delivery and consistently high evaluations created opportunities to lecture    

::: concise
- **GEOG1000: Human Settlements**: Develop practicals, workbooks, and assessments for over 200 first-year geography, environmental management, and urban planning students per semester, and manage and train up to 4 demonstrators running a portion of these practicals per semester
- **SOCY2339/7339: Introduction to Quantitative Methods**: Develop and deliver introductory statistical modelling workshops using Stata for over 60 second-year and 20 research by higher degree students per semester
- **SOCY2340: Sociology of the City**: Tutor across urban topics including public space, social equity, community sociability, and environmental criminology to over 60 second-year sociology, criminology, urban planning, and geography students per semester
- **CRIM1000: Introduction to Criminology** Develop and deliver introductory criminology tutorials to over 60 first-year criminology students per semester
:::

Professional Experience {data-icon=suitcase}
--------------------------------------------------------------------------------

### Invited Regional Active and Public Transport Advocacy Committee (RAPTAC) Member 

Toowoomba Regional Council (TRC)

Toowoomba, Australia

2025 (single term)

**Role**: Provide transport planning research, policy, and implementation recommendations for TRC's transport planning projects


### National Co-convenor Urban Data Science Network

The Planning Institute of Australia

Brisbane, Australia

ongoing - 2024 

**Role**: Developing a national framework for technical capabilities required from graduates and planning specialists

### PlanTech Committee Member

The Planning Institute of Australia

Brisbane, Australia

onging - 2023

**Role**: Developing a national framework for technical capabilities required from graduates and planning specialists


### The Early and Mid Career Researcher Representative

The University of Queensland’s Faculty of Science Research Committee

Brisbane, Australia

2020 - 2019

**Role**: Invited to represent EMCRs at monthly faculty research committee meetings chaired by the faculty Associate Dean of Research

### The Urban Planning and Geography Representative

The University of Queensland’s School of Earth and Environmental Sciences Early Career Researcher Committee

Brisbane, Australia

2020 - 2019

**Role**: Invited to represent urban planning and geography ECRs at monthly school meetings, develop grant guidelines and applications, and evaluate these applications

### Milestone and Thesis Examiner

N/A

N/A

2018

**Role**: Examine RhD milestones and theses on topics including environmental criminology, urban sociology, demography, land use and transport planning, and urban ecology 

### Academic Journal Reviewer

N/A

N/A

2015 - present

**Role**: Peer-reviewer for journals including: *Applied Geography; Applied Spatial Analysis and Policy; Australian Planner; Behavioural Research Methods; City, Culture and Society; Ecosystem Services; Environment and Behaviour; Environment and Planning B: Urban Analytics and City Science; Environmental Planning and Management; Geoforum; Housing and the Built Environment; Land Use Policy; Landscape and Urban Planning; Landscape Research; Population Research; Research in Crime and Delinquency; Security Journal; Social Science Research; Spatial Science; Springer Nature: Social Science; Sustainability; Sustainable Cities and Society; Transport Reviews; Travel Behaviour and Society; Urban Studies; and Urbanism: International Research on Placemaking and Urban Sustainability*


Publications   {data-icon=file}
--------------------------------------------------------------------------------

### Overall (Google Scholar `r format(Sys.time(), '%d/%m/%y')`)

Total cites = `r total_cites` and h-index = `r round(h_index,0)`

N/A

Current


`r x <- 1`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


`r x <- 2`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


`r x <- 3`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 4`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 5`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 6`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 7`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 8`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 9`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 10`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 11`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


`r x <- 12`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


`r x <- 13`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 14`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 15`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 16`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 17`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 18`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 19`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 20`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 21`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


`r x <- 22`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


`r x <- 23`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 24`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 25`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 26`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 27`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`

`r x <- 28`

### `r pub_stat("formatted_title")`

`r pub_stat("formated_journal")`

N/A

`r pub_stat("year")`

`r pub_stat("author")`


Conference Presentations {data-icon=microphone}
--------------------------------------------------------------------------------

###  [Chair City Movement and Infrastructure Track](https://absoluteevents.eventsair.com/soac2025/track-co-chairs)

State of Australian Cities 2025

Brisbane, Australia

2025

**A. Kimpton**

### [Assessing our 10/15/20/30-minute cities/neighbourhoods policy outcomes](https://www.aitpm.com.au/events/online-conference-series/2024-25-online-technical-conference-series/sessions/view-session-reimagining-urban-form-parking-accessibility-and-emerging-technolog)

AITPM Online Technical Conference Series

Online

2025

**A. Kimpton**

### [Multimodal Routing Methods for Supporting Sustainable Mobilities](https://www.aitpm.com.au/events/current-events/qld-2/qld-2024/toowoomba-technical-seminar-wednesday-5-june-2024)

AITPM Toowoomba Technical Seminar

Toowoomba, Australia

2024

**A. Kimpton**

### [Introduction to chrono-urbanism and spatial networks in R](https://resbaz.github.io/resbaz2023qld/speakers/)

ResBazQld 2023

Brisbane, Australia

2023

**A. Kimpton**


### Capturing Change to Daily Mobility (and Immobility)

eResearch Australasia Conference

Brisbane, Australia

2019

**A. Kimpton**

### Contemporary Parking Policy and Practice in Large Australian Cities

International Geographical Union

L’Aquila, Italy

2019 

**A. Kimpton**, D. Pojani, C. Ryan, L. Ouyang, J. Corcoran, & N. Sipe 

### Urban Immobility

International Geographical Union

Quebec, Canada

2018

**A. Kimpton**, J. Corcoran, D. Pojani, & N. Sipe

### By Invitation Only: Private and Public Space, Neighborhood Social Cohesion and Crime

American Society of Criminology Conference

Atlanta G.A., United States

2018

**A. Kimpton**, J. Corcoran, & R. Wickes

### The Duality of Neighborhood Social Conduits: A Case Study of Greenspace Crime

American Society of Criminology Conference

Philadelphia P.A., United States

2017

**A. Kimpton**, J. Corcoran, J. Hipp, R. Wickes, & R. Zahnow

### Public Greenspaces and Crime

American Society of Criminology Conference

Washington D.C, United States

2015

**A. Kimpton**, J. Corcoran, & R. Wickes

### Public Greenspaces and Crime: An Analysis of Crime Timing and Public Greenspace Amenities

State of Australian Cities Conference

Gold Coast, Australia

2015

**A. Kimpton**, J. Corcoran, & R. Wickes

### Perspectives on Resilience: A Case Study of the 2011 Brisbane Floods

Disaster and Emergency Management Conference

Gold Coast, Queensland

2014

**A. Kimpton** & J. Corcoran

Professional Membership  {data-icon=id-card}
--------------------------------------------------------------------------------

### The Planning Institute Australian

N/A

N/A

N/A

### The Australian Institute of Traffic Planning and Management

N/A

N/A

N/A

### The Institute of Australian Geographers

N/A

N/A

N/A

### The International Geographical Union

N/A

N/A

N/A

Other Skills and Qualifications {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

### Asymmetric Innovations' Impact Forge

N/A

N/A

2020

### Writing for The Conversation

N/A

N/A

2019

### Science Communication and Mainstream Media

N/A

N/A

2019

### Alternate Futures' Industry Engagement Program

N/A

N/A

2019

### Software Carpentry with Python

N/A

N/A

2017

### Complete Python Bootcamp

N/A

N/A

2016

### Stata Programming Workshop

N/A

N/A

2016

### Multilevel Modelling Course

N/A

N/A

2015

### Open Knowledge Brisbane Data Visualisation Workshop

N/A

N/A

2014

### Envirohack Workshop

N/A

N/A

2013

### Tutors\@UQ Program

N/A

N/A

2013

Referees  {data-icon=phone}
--------------------------------------------------------------------------------

### Professor Jonathan Corcoran

Deputy Associate Dean of Science and Director of the Queensland Centre for Population Research

N/A

N/A

**Mail**: Room 512, Level 5, Chamberlain Building (#35), University of Queensland, St Lucia, Queensland, Australia, 4067

**Phone**: (+61) 733 656 517

**Email**: [jj.corcoran@uq.edu.au](jj.corcoran@uq.edu.au)

### Professor Rebecca Wickes

Director of the Griffith Criminology Institiute

N/A

N/A

**Mail**: School of Criminology and Criminal Justice, Griffith University, Mount Gravatt, Queensland, Australia,  4122

**Phone**: (+61) 413 623 929

**Email**: [r.wickes@griffith.edu.au](r.wickes@griffith.edu.au)

### Emeritus Professor Neil Sipe

Former School Head of Urban and Regional Planning

N/A

N/A

**Mail**: Chamberlain Building (#35), University of Queensland, St Lucia, Queensland, Australia, 4067

**Phone**: (+61) 427 958 566

**Email**: [n.sipe@uq.edu.au](n.sipe@uq.edu.au)

